\section{Evaluation}
We show that given an interested SDN (sub)network with rules $SN(R)$, our approach can 
(1) transform $SN(R)$ to a single OpenFlow switch without any loss of forwarding logic in network $SN(R)$;
(2) save emulation resources such as number of total rules in the network and emulation runtime.

In this section, we consider a tree topology with two topological parameters: depth $d$ and fanout $f$.
Such a tree network $tree(d, f)$ can connect $f^d$ hosts with $\frac{f^d - 1}{f-1}$ switches in total.
Though not known as a scalable network architecture
(a good scalable alternative will be fat-tree topology),
it is good for demonstrational purpose since the tree topology is well-structured and
all hosts in it are potentially fully-connected with at most $2d$ hops.

\subsection{Preserve Forwarding Logic}
We generate forwarding logic in tree-topology network by connecting random host pairs.
One can find the shortest path between a pair of hosts $(s, d)$ with
a layer-two learning switch controller application.
Traversing the tree up and down in breadth-first-search style, learning switch application
will automatically install OpenFlow rules on each hop when we initiate \texttt{ping} between
the given pair of host.
More specifically, we start a tree-topology network in Mininet\cite{Mininet},
connecting all switches to a l2\_learning\cite{pox} controller.
For any network host $s$, we randomly generate a list of distinct hosts $dsts$,
then let $s$ \texttt{ping} each host $\in dsts$.
After doing the \texttt{ping} process for all hosts, we take a snapshot of this network by
\begin{enumerate}
\item Record the network topology, e.g. host to switch and switch to switch connections.
\item Log out all rules on all switches with \texttt{ovs-ofctl dump-flows} command
\end{enumerate}
We feed the above information as input and generate the rules of the new big switch
and port mapping according to procedures and algorithms presented in section~\ref{Sec:Design}.

To proof that our approach can preserve the existing forwarding logic,





\subsection{Resource Reduction}

