\section{Related Work}

\subsection{Network Forwarding Rules Abstraction}
This work is initially inspired by the "one big switch" idea proposed
in \cite{OneBigSwitchAbstraction}.
The entire SDN network are logically abstracted as one big OpenFlow switch such
that network developers just need to specify the end-to-end policies they want
to install into the network.
Underlying, the lower layers are responsible for address various implementation
issues such as hop-by-hop routing rules and rule placement mechanism.
In their work, the end-to-end policy is given by network applications.
Our work actually takes the reversed direction: we assume the forwarding rules on each
switch are available and we want to correctly infer the end-to-end policies.
Our three-step approach borrows several ideas like equivalence class, forwarding graphs
from VeriFlow\cite{Veriflow}, to slice the class of packets in the network.
There are, however, many significant differences between our approach and VeriFlow.
First VeriFlow uses EC and forwarding graphs so that verifying a new coming rule can be
both efficient and correct;
our goal is to generate rule on the big switch per packet class.
Secondly, we consider the entire connected SDN network when we run forwarding traversal,
especially the boundary switches that Veriflow neglects.
We also add up several algorithms in finding equivalence classes.

\subsection{SDN Emulation and Simulation}
There are a number of SDN emulation and simulation testbeds based on the OpenFlow
protocol.
Examples include Mininet\cite{Mininet}, EstiNet\cite{Estinet}, ns-3\cite{NS3},
S3FNet\cite{S3F}, fs-sdn\cite{FSSDN} and OpenNet\cite{OpenNet}.
The most popular SDN emulator Mininet applies container-based virtualization technique
and cgroup based resource isolation to provide lightweigth and high fidelity emualtion
platform.
Its functional fidelity is guaranteed by executing real SDN switch and controller software.
The traditional network simulator ns-3 supports models to simulate SDN network or emulate SDN
controller via direct code execution technique.
S3FNet is a hybrid OpenFlow-based SDN testing platform that integrates a parallel
network simulator with a OpenVZ-based network emulator.
fs-sdn is built on fs, a flow-level discrete event network simulator, and extends SDN
capability to fs.
We propose a systematic method to simplify the large scale and complicated SDN network target.
It serves as a preprocessing tool that generate a compact network model.
This resulting big-switch network can be used in both simulation and emulation environment
and its usage is not limited by any particular emulator or simulator.
